---
title: "BSA_Manuscript"
author: "Vera Miyase Yilmaz"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      warning = FALSE)
```

# Bulk Segregant Analysis

The aim of the analysis is to determine the variants that are related to
chill coma recovery time (CCRT) phenotype. Four pools were used for the
analysis: \* Tolerant parental line pool: BKK12 \* Sensitive parental
line pool: BKK13 \* Extremely tolerant offspring pool: CCRT \< 30
minutes \* Extremely sensitive offspring pool: CCRT \> 60 minutes

100 females for each of the parental pools were collected from F2
generation. For extreme phenotype offspring pools, the females of
F2 generation were collected and kept at rearing temperature on standard
corn molasses medium until they were 4-6 days old. The single flies were
transferred into empty vials and placed on ice for 3 hours to induce
chill coma. Then, the vials were placed back to the rearing temperature
for recovery. The flies that were able to stand in the first 30 minutes
were collected as extremely-fast-recovering offspring. The flies that
were able to stand in the second 30 minutes were discarded. At the end
of the third and the last 30 minutes, the alive flies were collected as
the extremely-slow-recovering offspring regardless of their recovery
state. The chill coma recovery assay was repeated until 100 flies were
collected for each offspring pool.

The flies were placed into 1.5mL eppendorf tubes in groups of 10 and
snap-frozen in liquid nitrogen for DNA extraction. The DNA was extracted
using MasterPure™ DNA Purification Kit (Epicentre, Madison, WI, USA).
The DNA samples were pooled together and sent for whole genome
sequencing to an external facility (Novogene, Cambridge, UK), which
performed high-throughput sequencing using a Novaseq 6000 sequencer
(Illumina, San Diego, CA, USA) to generate 150-bp paired-end reads. On
average 62.4 million reads were generated per sample.

The raw data was mapped to Drosophila ananassae genome (NCBI Drosophila
ananassae Annotation Release 102) using the Burrows-Wheeler Aligner tool
(version 0.5.0). Further processing -sorting, merging, duplicate
removing- was done using samtools (version 1.18). Variant calling was
performed using freebayes (version 1.3.8). The variants were filtered
using bcftools (version 1.18). Finally, GATK-VariantsToTable tool was
used to prepare the data for further analysis on R (version 4.2.2).

```{r packages, include=FALSE}
setwd('/Users/verayilmaz/Desktop/BSA')
library(vcfR)
library(QTLseqr)
library(dplyr)
library(tidyr)
library(readr)
library(readxl)
library(ggplot2)
library(ggpubr)
library(GenomicRanges)
library(rtracklayer)
library(clusterProfiler)
library(genekitr)
library(org.Dm.eg.db)
library(AnnotationDbi)
```

## Import Data

We import the .table files that contain the variants of each pool. These
files were generated using GATK VariantsToTable tool. The headers of
columns are:

1.  CHROM

2.  POS

3.  REF

4.  ALT

5.  QUAL

6.  DP

7.  TolerantOffspring.GT

8.  TolerantOffspring.AD

9.  TolerantOffspring.DP

10. TolerantOffspring.GQ -\> this one we do not need and therefore
    removed from the table.

We also import the tables that include the ortologous gene list and the
REFSEQ numbers that correspond the FlyBase numbers.

After removing the unwanted column, we combine the desired sample pools
together. For parental comparison, we combine the tolerant
(fast-recovering) and sensitive (slow-recovering) parental pools. For
offspring comparison, we combine all the pools together, because the
further analysis takes the parental differences into consideration and
explains the main differences between the two extreme phenotypes.

We save the new data frames into a new file with .table extension to be
able to use it with `importFromGATK()` function

```{r data, echo=FALSE}
poolTO <- read_tsv("tolerant_offspring2.table") # tolerant offspring
poolTO <- poolTO[,-10]
poolTP <- read_tsv("tolerant_parent2.table") # tolerant parent
poolTP <- poolTP[,-10]
poolSO <- read_tsv("sensitive_offspring2.table") # sensitive offspring
poolSO <- poolSO[,-10]
poolSP <- read_tsv("sensitive_parent2.table") # sensitive parent
poolSP <- poolSP[,-10]
extracted2 <- read_tsv("REFSEQ_FLYBASE_Dana.txt")
ortholog <- read_excel("dmel_dana_orthologs.xlsx")
orthologs<-AnnotationDbi::select(org.Dm.eg.db,keys = ortholog$ortholog, keytype = "FLYBASE",columns = c("FLYBASE", "ENTREZID")) %>%
  dplyr::right_join(ortholog, by = c("FLYBASE" = "ortholog"))
annotation <- import("Dana_annotation.gtf")
```

```{r field_names, include=FALSE}
chromosomes <- c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1")
# NC_057927.1: chromosome 2L
# NC_057928.1: chromosome 2R
# NC_057929.1: chromosome 3L
# NC_057930.1: chromosome 3R
# NC_057931.1: chromosome XL
# NC_057932.1: chromosome XR
### Sensitive and tolerant parents combined
parent_pools <- dplyr::full_join(poolTP[,-5:-6], poolSP[,-5:-6])
write_tsv(parent_pools, "parent_pools.table")
SNPset_parent <- importFromGATK("parent_pools.table", 
                                   highBulk = "TolerantParent", lowBulk = "SensitiveParent",
                                   chromList = chromosomes)
### all pools combined - offsprings are high-low bulks
tolerant_pools <- dplyr::full_join(poolTP[,-5:-6], poolTO[,-5:-6])
sensitive_pools <- dplyr::full_join(poolSP[,-5:-6], poolSO[,-5:-6])
all_pools <- dplyr::full_join(tolerant_pools, sensitive_pools)
write_tsv(all_pools, "all_pools.table")
SNPset_all <- importFromGATK("all_pools.table", 
                             highBulk = "TolerantOffspring", lowBulk = "SensitiveOffspring", 
                             chromList = chromosomes)
```

## Analysis

Now we perform

-   the QTL analysis and generate the plots for "No of SNPs in 1Mb
    window" and "delta-SNP index"
    -   SNP index (∆SNP) refers to the subtraction of the alternate
        allele frequency value of the low bulk from the high bulk (∆SNP)
-   the G' analysis and generate the associated plots
    -   G-statistics takes advantage of a log-likelihood statistic LOD
        between allele frequencies

### SNPset - all pools

```{r}
SNPset <- SNPset_all
SNPset_filtered <- filterSNPs(SNPset, refAlleleFreq = 0.3, minTotalDepth = 40, maxTotalDepth = 400, depthDifference = 50, verbose = TRUE)
SNPset_nona <- na.omit(SNPset_filtered)
qtl <- runQTLseqAnalysis(SNPset_nona, bulkSize = 100,
                         windowSize = 1e6, 
                         popStruc = "RIL")
qtl2 <- qtl
qtl$CHROM <- factor(qtl$CHROM, levels = c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1"), labels = c("Chr 2L", "Chr 2R", "Chr 3L", "Chr 3R", "Chr XL", "Chr XR"))
gprime <- runGprimeAnalysis(SNPset_nona, windowSize = 1e6)
gprime2 <- gprime
gprime$CHROM <- factor(gprime$CHROM, levels = c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1"), labels = c("Chr 2L", "Chr 2R", "Chr 3L", "Chr 3R", "Chr XL", "Chr XR"))
```

```{r all_pools, echo=FALSE, fig.height=8, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
nSNPs_plot <- plotQTLStats(qtl) + theme_minimal()
deltaSNP_plot <- plotQTLStats(qtl, var = "deltaSNP", plotIntervals = TRUE) + theme_minimal() + theme(legend.position = "bottom") + scale_color_manual(values = c("grey", "red"))
gprime_plot <- plotQTLStats(gprime, var = "Gprime", plotThreshold = T) + theme_minimal()
cowplot::plot_grid(nSNPs_plot, deltaSNP_plot, gprime_plot, nrow = 3, labels = "AUTO", rel_heights = c(0.8, 0.8, 1), align = "v")
```

```{r all_pools_ind_plot, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
nSNPs_plot
deltaSNP_plot
gprime_plot
```

Now, we can obtain the significant regions associated with the trait.
These regions are significantly different between the extreme-phenotype
offsprings.

```{r}
sigRegions_qtl <- getSigRegions(qtl, method = "QTLseq")
sigRegions_gprime <- getSigRegions(gprime, method = "Gprime", alpha = 0.05)
rownames(summary(sigRegions_qtl))
rownames(summary(sigRegions_gprime))
paste0(length(rownames(summary(sigRegions_qtl))), " significant QTL regions")
paste0(length(rownames(summary(sigRegions_gprime))), " significant G' regions")
```

#### Annotation

For the gene information of the significant regions, we use the genome
annotation provided with the reference genome. To find the gene names in
the given significant regions, we first simplify the data. We need the
sequence names, starting position, and the final position of the
significant region.

Using `makeGRangesFromDataFrame()`, `findOverlaps()`, and
`annotation[subjectHits()]` functions, we identify the genes in the
significant regions. For further analysis (i.e. GO analysis), the *D.
melanogaster* orthologs are used.

```{r}
sigQTL <- getQTLTable(qtl2, method = "QTLseq", export = T, fileName = "sigQTL.csv")
sigQTL_positive <- sigQTL[which(sigQTL$avgDeltaSNP > 0),1:4]
sigQTL_negative <- sigQTL[which(sigQTL$avgDeltaSNP < 0),1:4]

# positive
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_positive[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmelpositive <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmelpositive, "positive_ogenes_dmel.tsv")

# negative
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_negative[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmelnegative <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmelnegative, "negative_ogenes_dmel.tsv")

# all
sigQTL_short <- sigQTL[,1:4]
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_short[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmel <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmel, "all_ogenes_dmel.tsv")
```

```{r positiveGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmelpositive
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

```{r negativeGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmelnegative
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

```{r allGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmel
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

