---
title: "Heatwave RNA-seq: Results overview"
author: "Vincent Ohlhauser"
engine: knitr
highlight-style: github
mainfont: "roboto"
format: 
  html: 
    theme: cosmo 
    toc: true
    toc_float: true 
    toc-location: left
    code-fold: true
    code-tools: true
    embed-resources: true
    number-sections: true
    number-depth: 3
    linkcolor: "green"
    mermaid: 
      theme: neutral
date: last-modified
date-format: full
execute:
  echo: true
  warning: false
  message: false
  cache: true
  output: true
code-overflow: scroll
code-line-numbers: true
code-copy: hover
---

```{mermaid}
%%| echo: false
%%| label: fig-flowchart1
%%| fig-cap: General overview of analysis from raw reads to variant table. Code for this is missing!

flowchart LR
    A(Sequencing) --> B(Mapping BWA)
    B --> C(Filter, format samtools)
    C --> D(Variant calling freebayes)
    D --> E(Filter bcftools)
    E --> F(Export to R GATK)
```

```{mermaid}
%%| echo: false
%%| label: fig-flowchart2
%%| fig-cap: General overview of analysis from variant table to enriched regions and genes. Includes visualizations after each step. Code available!

flowchart LR
    A(Import and format data) --> B(QTL and G` analysis)
    B --> C(Get enriched regions)
    C --> D(GO term enrichment)
```

```{r}
#| label: setup
source("../scripts/_install_packages.R", local = FALSE)
```

## Import Data

We import the .table files that contain the variants of each pool. These
files were generated using GATK VariantsToTable tool. The headers of
columns are:

1. CHROM -> chromosome
2. POS -> position
3. REF -> reference sequence
4. ALT -> alternative sequence
5. \*.AD -> allelic depths
6. \*.DP -> read depth
7. \*.GT -> genotype call
8. QUAL -> not in my files, variant level quality score
9. TolerantOffspring.GQ -> not in my files, genotype quality

We also import the tables that include the ortologous gene list and the
REFSEQ numbers that correspond the FlyBase numbers.

After removing the unwanted column, we combine the desired sample pools
together. For parental comparison, we combine the tolerant
(fast-recovering) and sensitive (slow-recovering) parental pools. For
offspring comparison, we combine all the pools together, because the
further analysis takes the parental differences into consideration and
explains the main differences between the two extreme phenotypes.

We save the new data frames into a new file with .table extension to be
able to use it with `importFromGATK()` function

```{r}
#| label: import data
#| eval: false
#| code-summary: Import data, format, write to file
# ---- 2. Load input data ----
pool_Tolerant_Offspring <- read.delim(file.path("data", "raw", "fast_O.table"))
pool_Sensitive_Offspring <- read.delim(file.path("data", "raw", "slow_O.table"))
pool_Tolerant_Parent <- read.delim(file.path("data", "raw", "fast_P.table"))
pool_Sensitive_Parent <- read.delim(file.path("data", "raw", "slow_P.table"))

# ---- 3. Rename columns for clarity ----
rename_columns <- function(df, prefix) {
  names(df)[names(df) == "sample01.AD"] <- paste0(prefix, ".AD")
  names(df)[names(df) == "sample01.DP"] <- paste0(prefix, ".DP")
  names(df)[names(df) == "sample01.GT"] <- paste0(prefix, ".GT")
  return(df)
}

pool_Tolerant_Offspring <- rename_columns(pool_Tolerant_Offspring, "TolerantOffspring")
pool_Sensitive_Offspring <- rename_columns(pool_Sensitive_Offspring, "SensitiveOffspring")
pool_Tolerant_Parent <- rename_columns(pool_Tolerant_Parent, "TolerantParent")
pool_Sensitive_Parent <- rename_columns(pool_Sensitive_Parent, "SensitiveParent")

# ---- 4. Merge pools ----
a <- full_join(pool_Sensitive_Offspring, pool_Sensitive_Parent)
b <- full_join(pool_Tolerant_Offspring, pool_Tolerant_Parent)
c <- full_join(a,b)
write_tsv(c, file.path("data", "processed", "offspring_pools.table"))
```

## Analysis

Now we perform

-   the QTL analysis and generate the plots for "No of SNPs in 1Mb
    window" and "delta-SNP index"
    -   SNP index (∆SNP) refers to the subtraction of the alternate
        allele frequency value of the low bulk from the high bulk (∆SNP)
-   the G' analysis and generate the associated plots
    -   G-statistics takes advantage of a log-likelihood statistic LOD
        between allele frequencies

### SNPset - all pools

```{r}
#| label: import-pools
#| eval: false

# ---- 5. Define analysis parameters ----
file <- file.path("data", "processed", "offspring_pools.table")
Chroms <- c("CM029943.2", "CM029944.2", "CM033063.1", "CM033064.1", "CM029945.2", "CM029946.2")
HighBulk <- "TolerantOffspring"
LowBulk <- "SensitiveOffspring"

# ---- 6. Import SNP data ----
SNPset <- QTLseqr::importFromGATK(file = file, highBulk = HighBulk, 
                     lowBulk = LowBulk, chromList = Chroms)

# ---- 8. Filter SNPs ----
SNPset_filt <- QTLseqr::filterSNPs(SNPset = SNPset, 
                      refAlleleFreq = 0.20, 
                      depthDifference = 100, 
                      maxTotalDepth = 400, 
                      verbose = TRUE)
SNPset_nona <- na.omit(SNPset_filt)
```


```{r}
SNPset <- SNPset_all
SNPset_filtered <- filterSNPs(SNPset, refAlleleFreq = 0.3, minTotalDepth = 40, depthDifference = 50, verbose = TRUE)
SNPset_nona <- na.omit(SNPset_filtered)
qtl <- runQTLseqAnalysis(SNPset_nona, bulkSize = 100,
                         windowSize = 1e6, 
                         popStruc = "RIL")
qtl2 <- qtl
qtl$CHROM <- factor(qtl$CHROM, levels = c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1"), labels = c("Chr 2L", "Chr 2R", "Chr 3L", "Chr 3R", "Chr XL", "Chr XR"))
gprime <- runGprimeAnalysis(SNPset_nona, windowSize = 1e6)
gprime2 <- gprime
gprime$CHROM <- factor(gprime$CHROM, levels = c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1"), labels = c("Chr 2L", "Chr 2R", "Chr 3L", "Chr 3R", "Chr XL", "Chr XR"))
```

```{r all_pools, echo=FALSE, fig.height=8, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
nSNPs_plot <- plotQTLStats(qtl) + theme_minimal()
deltaSNP_plot <- plotQTLStats(qtl, var = "deltaSNP", plotIntervals = TRUE) + theme_minimal() + theme(legend.position = "bottom") + scale_color_manual(values = c("grey", "red"))
gprime_plot <- plotQTLStats(gprime, var = "Gprime", plotThreshold = T) + theme_minimal()
cowplot::plot_grid(nSNPs_plot, deltaSNP_plot, gprime_plot, nrow = 3, labels = "AUTO", rel_heights = c(0.8, 0.8, 1), align = "v")
```

```{r all_pools_ind_plot, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
nSNPs_plot
deltaSNP_plot
gprime_plot
```

```{r}
#| label: leftover-code
#| eval: false

# Get additional files into renv
extracted2 <- read_tsv("REFSEQ_FLYBASE_Dana.txt")
ortholog <- read_excel("dmel_dana_orthologs.xlsx")
orthologs<-AnnotationDbi::select(org.Dm.eg.db,keys = ortholog$ortholog, keytype = "FLYBASE",columns = c("FLYBASE", "ENTREZID")) %>%
  dplyr::right_join(ortholog, by = c("FLYBASE" = "ortholog"))
annotation <- import("Dana_annotation.gtf")

# write pools to table
chromosomes <- c("NC_057927.1", "NC_057928.1", "NC_057929.1", "NC_057930.1", "NC_057931.1", "NC_057932.1")
# NC_057927.1: chromosome 2L
# NC_057928.1: chromosome 2R
# NC_057929.1: chromosome 3L
# NC_057930.1: chromosome 3R
# NC_057931.1: chromosome XL
# NC_057932.1: chromosome XR
### Sensitive and tolerant parents combined
parent_pools <- dplyr::full_join(poolTP[,-5:-6], poolSP[,-5:-6])
write_tsv(parent_pools, "parent_pools.table")
SNPset_parent <- importFromGATK("parent_pools.table", 
                                   highBulk = "TolerantParent", lowBulk = "SensitiveParent",
                                   chromList = chromosomes)
### all pools combined - offsprings are high-low bulks
tolerant_pools <- dplyr::full_join(poolTP[,-5:-6], poolTO[,-5:-6])
sensitive_pools <- dplyr::full_join(poolSP[,-5:-6], poolSO[,-5:-6])
all_pools <- dplyr::full_join(tolerant_pools, sensitive_pools)
write_tsv(all_pools, "all_pools.table")
SNPset_all <- importFromGATK("all_pools.table", 
                             highBulk = "TolerantOffspring", lowBulk = "SensitiveOffspring", 
                             chromList = chromosomes)
```

Now, we can obtain the significant regions associated with the trait.
These regions are significantly different between the extreme-phenotype
offsprings.

```{r}
sigRegions_qtl <- getSigRegions(qtl, method = "QTLseq")
sigRegions_gprime <- getSigRegions(gprime, method = "Gprime", alpha = 0.05)
rownames(summary(sigRegions_qtl))
rownames(summary(sigRegions_gprime))
paste0(length(rownames(summary(sigRegions_qtl))), " significant QTL regions")
paste0(length(rownames(summary(sigRegions_gprime))), " significant G' regions")
```

#### Annotation

For the gene information of the significant regions, we use the genome
annotation provided with the reference genome. To find the gene names in
the given significant regions, we first simplify the data. We need the
sequence names, starting position, and the final position of the
significant region.

Using `makeGRangesFromDataFrame()`, `findOverlaps()`, and
`annotation[subjectHits()]` functions, we identify the genes in the
significant regions. For further analysis (i.e. GO analysis), the *D.
melanogaster* orthologs are used.

```{r}
sigQTL <- getQTLTable(qtl2, method = "QTLseq", export = T, fileName = "sigQTL.csv")
sigQTL_positive <- sigQTL[which(sigQTL$avgDeltaSNP > 0),1:4]
sigQTL_negative <- sigQTL[which(sigQTL$avgDeltaSNP < 0),1:4]

# positive
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_positive[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmelpositive <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmelpositive, "positive_ogenes_dmel.tsv")

# negative
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_negative[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmelnegative <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmelnegative, "negative_ogenes_dmel.tsv")

# all
sigQTL_short <- sigQTL[,1:4]
granges_sig_regions <- makeGRangesFromDataFrame(sigQTL_short[,-2], keep.extra.columns = TRUE)
overlaps <- findOverlaps(granges_sig_regions, annotation)
overlapping_genes <- annotation[subjectHits(overlaps)]
ogenes <- as.data.frame(unique(overlapping_genes@elementMetadata@listData[["transcript_id"]]))
colnames(ogenes) <- "refseq"
ogenes <- ogenes %>% separate(refseq, c("REFSEQ1", "REFSEQ2"), "_")
ogenes <- ogenes[which(ogenes$REFSEQ1 == "XM"),]
ogenes2 <- ogenes %>% separate(REFSEQ2, c("REFSEQ2"))
ogenes <- unite(ogenes2, col = "REFSEQ",REFSEQ1:REFSEQ2, sep = "_")
ogenes_FB <- merge(x = ogenes, y = extracted2, by = "REFSEQ")
colnames(ogenes_FB) = c("REFSEQ", "Dana_ID")
ogenes_dmel <- merge(x = ogenes_FB, y = orthologs, by = "Dana_ID")
write_tsv(ogenes_dmel, "all_ogenes_dmel.tsv")
```

```{r positiveGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmelpositive
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

```{r negativeGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmelnegative
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

```{r allGO, echo=FALSE, fig.height=5, fig.path="ManuscriptFigures/", fig.width=8,  dev='pdf'}
result <- ogenes_dmel
gseGO_BP <- enrichGO(gene = result$ENTREZID, ont = "BP", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
BP <- gseGO_BP@result[which(gseGO_BP@result$p.adjust < 0.05),]
gseGO_MF <- enrichGO(gene = result$ENTREZID, ont = "MF", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
MF <- gseGO_MF@result[which(gseGO_MF@result$p.adjust < 0.05),]
gseGO_CC <- enrichGO(gene = result$ENTREZID, ont = "CC", OrgDb = org.Dm.eg.db, readable = T, pAdjustMethod = "fdr", pvalueCutoff = 0.01)
CC <- gseGO_CC@result[which(gseGO_CC@result$p.adjust < 0.05),]
#
if (length(BP$GeneRatio) > 0) {
tmp <- BP[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
BP$GeneRatio <- BP$Count/tmp$Total
BP$Ontology <- "BP"
} else {
    paste0("no significant enricment of BP terms are found")
}
if (length(MF$GeneRatio) > 0) {
tmp <- MF[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
MF$GeneRatio <- MF$Count/tmp$Total
MF$Ontology <- "MF"
} else {
    paste0("no significant enricment of MF terms are found")
}
if (length(CC$GeneRatio) > 0) {
tmp <- CC[1,] %>% separate(GeneRatio, c(NA, "Total"), "/", convert = T)
CC$GeneRatio <- CC$Count/tmp$Total
CC$Ontology <- "CC"
} else {
    paste0("no significant enricment of CC terms are found")
}
if (length(BP$GeneRatio) > 0) {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(rbind(BP, MF), CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO <- rbind(BP, MF)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#BC3C29FF", "#E18727FF"))
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(BP, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    } else {
      GO_plot <- plotEnrich(BP, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35)
    }
  }
} else {
  if (length(MF$GeneRatio) > 0) {
    if (length(CC$GeneRatio) > 0) {
      GO <- rbind(MF, CC)
      GO_plot <- plotEnrich(GO, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = c("#E18727FF", "#0072B5FF"))
    } else {
      GO_plot <- plotEnrich(MF, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#E18727FF")
    }
  } else {
    if (length(CC$GeneRatio) > 0) {
      GO_plot <- plotEnrich(CC, plot_type = "wego", n_term = 15, term_metric = "GeneRatio", wrap_length = 35) + scale_fill_manual(values = "#0072B5FF")
    } else {
      paste0("No plot drawn due to lack of significant GO terms")
    }
  }
}
if (length(BP$GeneRatio) == 0 & length(MF$GeneRatio) == 0 & length(CC$GeneRatio) == 0) {
  paste0("No plot drawn due to lack of significant GO terms")
  GO_plot <- NULL
} else {
  GO_plot <- ggpar(GO_plot, font.tickslab = 6)
  GO_plot[["facet"]][["params"]][["space_free"]][["x"]] <- FALSE
}
GO_plot
```

